\documentclass{resume} 

\usepackage[left=0.1in,top=0.1in,right=0.1in,bottom=0.1in]{geometry}
\usepackage[utf8]{vietnam}
\usepackage{changepage}
\usepackage{booktabs}
\usepackage{enumitem}

\title{PhamDaoCongThanh_Fullstack-Software-Engineer}
\begin{document}

\begin{center}
    \section*{Phạm Đào Công Thành}
\end{center}

\begin{center}
    Full-stack Software Engineer 
\end{center}

\begin{center}
    \begin{tabular}{ll}
        Email: \href{mailto:pdcthanh112.dev@gmail.com}{pdcthanh112.dev@gmail.com} & GitHub: \href{github.com/pdcthanh112}{github.com/pdcthanh112} \\
        Phone: 0382 722 849 & LinkedIn: \href{linkedin.com/in/pdcthanh112dev}{ linkedin.com/in/pdcthanh112dev} \\
    \end{tabular}
\end{center}

\begin{center}
    \hrulefill{}
\end{center}

\section*{\begin{center}
    CAREER GOALS
\end{center}}
\begin{adjustwidth}{0.15in}{0.15in}
    \hspace{0.7cm}With what I have been trained in school, I look forward to finding opportunities to use the knowledge that I have accumulated over the years to contribute to the development of the company. I want to learn new knowledge and improve myself every day through working and contributing to the company, so I want to join this professional working environment. My short-term goal is to become a Full-stack developer, and long-term is to aim to be a DevOps engineer in the future.
\end{adjustwidth}

\section*{\begin{center}
    EDUCATION
\end{center}}
\textbf{FPT University HCM} -- Bachelor’s degree \hfill Aug 2018 - Oct 2022 \\
- Major: Software Engineering \\
- Specialization: Information System \\

\textbf{University of Science, VNUHCM} -- Master’s degree \hfill Mar 2023 - Now \\
- Major: Computer Science \\
- Specialization: Artificial Intelligence and Data Science \\

\section*{\begin{center}
    SUMMARY
\end{center}}
\begin{adjustwidth}{0.2in}{0.1in}
    \begin{itemize}
        \item Knowledge about C/C++, HTML/CSS, JavaScript, Typescript, Java, PHP, Python, Golang, Dart, R.
        \item Strong understanding of OOP methodologies, SOLID principles, and design patterns.
        \item Good knowledge about Data Structure and Algorithm.
        \item Work well with RESTful API standard, SOAP, GraphQL and gRPC.
        \item Availability design website following standards (W3C), responsive and well-interaction with SEO.
        \item Skilled in standard database design and know how to optimize queries.
        \item 3+ years of experience working with JavaScript/TypeScript as a Fullstack with React and NodeJS.
        \item Knowledge of working with Python for AI, machine learning, deep learning, and data processing.
    \end{itemize}
\end{adjustwidth}

\address{+1(123) 456-7890 \\ San Francisco, CA} 
\address{\href{mailto:contact@faangpath.com}{contact@faangpath.com} \\ \href{https://linkedin.com/company/faangpath}{linkedin.com/company/faangpath} \\ \href{www.faangpath.com}{www.faangpath.com}}  %

\section*{\begin{center}SKILLS\end{center}}
    \begin{tabular}{ll}
        % \toprule
        Programming language & HTML/CSS (HTML5/CSS3), Java, JavaScript/TypeScript (ES6+), Python, Golang \\
        \bottomrule
        Framework/Platform & 
        \begin{minipage}[t]{0.7\linewidth}
            \begin{itemize}[label={-}, leftmargin=0.4cm, itemsep=-0.2em]
                \item Backend: Spring framework, NodeJS, Express, NestJS, Laravel, Django
                \item Frontend: HTML/CSS (SCSS/SASS/LESS), React, NextJS, Angular, Vue, NuxtJS
                \item Desktop: Java Swing, ElectronJS
                \item Mobile: Java Android, Flutter, React Native, Ionic
                \item Other: Ajax, jQuery, Bootstrap, Tailwind CSS, Foundation, Ant Design, MUI, Flux/Redux
            \end{itemize}
        \end{minipage} \\
        \bottomrule
        Databases & 
        \begin{minipage}[t]{0.7\linewidth}
            \begin{itemize}[label={-}, leftmargin=0.4cm, itemsep=-0.2em]
                \item SQL: Microsoft SQL Server, MySQL, PostgreSQL, Oracle
                \item No-SQL: MongoDB, Cassandra, Neo4J
                \item Other: Redis, Elasticsearch, Firebase storage, SQLite
            \end{itemize}
        \end{minipage} \\
        \bottomrule
        Testing & Unit Test, Jest, Karma, Storybook, Selenium \\
        \bottomrule
        CI/CD & Jenkins, GitLab, Travis CI, CircleCI \\
        \bottomrule
        DevOps & Kubernetes, RabbitMQ, Kafka, Ansible, Terraform, Prometheus, Grafana, Elastic Stack \\
        \bottomrule
        Source control & Git, GitHub, GitLab, Bitbucket, SVN \\
        \bottomrule
        Cloud services & AWS, Microsoft Azure, Google Cloud Platform, Firebase, Digital Ocean \\
        \bottomrule
        Webserver & Apache, NginX, PM2, Microsoft IIS \\
        \bottomrule
        Operating system & Window (Window Server), Linux (Unix, Ubuntu, Kati Linux) \\
        \bottomrule
        IDE & Emacs, NeoVim, Visual Studio Code, Android Studio, IntelliJ, Jupyter Notebook \\
        \bottomrule
        Tool & Docker, Postman, Swagger, Figma, Photoshop, Jira Software, Jenkins \\
        \bottomrule
        Foreign languages & English (7.0 IELTS), Japanese (N4) \\
        \bottomrule
        Soft skills & Research \& self-learning, logical \& critical thinking, problem-resolving, teamwork \& leadership \\
        % \bottomrule
    \end{tabular}



\section*{\begin{center}
    CERTIFICATE
\end{center}}
\begin{adjustwidth}{0.2in}{0.2in}
    -	AWS Certified Developer - Associate (Amazon)\\
    -	Azure Solutions Architect Expert (Microsoft Certified)\\
    -	Microsoft Certified: DevOps Engineer Expert (Microsoft Certification)\\
    -	Google Certified Professional Cloud Architect (GCPCA)\\
    -	Continuous Integration and Continuous Delivery (CI/CD) (Coursera)\\
    -   Professional Certificate of Introduction to DevOps in Linux: Practices and Tools (edX)\\
    -   PSM Professional Scrum Master (Scrum.org)\\

\end{adjustwidth}



\section*{\begin{center}WORK EXPERIENCE\end{center}}
    \hspace{2cm}\textbf{\textbullet{} KMS Technology} {– Full-stack Software Engineer} \hfill \textit{Jan 2023 - Now} \\
    \textbf{\textit{Description:}} Working as a Full-stack Developer with various projects such as education, finance, e-commerce, payment platform, in these team:
    \begin{itemize}[label={-}, leftmargin=1cm, itemsep=-0.2em]
        \item KMS Technology focuses on custom software development and a wide variety of consulting services.
        \item KMS Healthcare specializes in the healthcare industry, provides a unique blend of consultative healthcare technology solutions backed by the power of full lifecycle development support.
        \item KMS Solutions serves the Asia Pacific region, bringing the world's innovative technologies to help organizations achieve their business goals through world-class digital capabilities and fit-for-purpose solutions.
    \end{itemize}
    \textbf{\textit{Responsibilities:}}
        \begin{itemize}[label={-}, leftmargin=1cm, itemsep=-0.2em]
            \item Ensure code quality and development practices are followed in a project team. Be a hands-on role model in that regard to technical team members.
            \item Stay on top of process and technological trends and help define \& enforce standards/practices within the project teams or companywide.
            \item Participate in pre-sale effort to build proof of concepts or develop project.
            \item Clarifying requirements with clients and the team.
            \item Writing high-quality code to implement software features or fix bugs and implementing unit tests.
            \item Ensure scalability, security, and performance of software systems.
            \item Collaborate with team members to identify and resolve software development and integration issues.
            \item Stay updated with the latest trends and techniques in AI and machine learning.
            \item Follow prescribed procedures and instructions to produce well-designed, testable, clean code.
        \end{itemize}
    \textbf{\textit{Technologies:}} ReactJS, NextJS, NodeJS, Angular, ElectronJS, MySQL, PostgreSQL, MongoDB, Docker, Jenkins, Git, AWS, Microsoft Azure, Google Cloud Platform, Firebase





    \hspace{2cm}\textbf{\textbullet{} NashTech Global} – Full-stack Developer \hfill \textit{Mar 2022 - Dec 2022} \\
    \textbf{\textit{Description:}} Build a system about applicant tracking system (ATS) and a website support recruitment request posting (similar to TopCV) to go-live.\\
    \textbf{\textit{Responsibilities:}}
        \begin{itemize}[label={-}, leftmargin=1cm, itemsep=-0.2em]
           \item Conduct guidelines, review architecture alternatives, perform technical evaluations including non-technical perspectives (security performance).
            \item Design, document and implement the architecture design on both detailed and high level with full awareness of the integration, maintenance, and migration aspects.
            \item Participate in database design and construction, assist in writing performance-optimized queries.
            \item Propose a technical development or training plan, follow, motivate, and support technical resources for skills development that meets personal, and company needs.
            \item Deploy applications to production environment using cloud services (Microsoft Azure, Digital Ocean, AWS, Google Cloud Platform).
        \end{itemize}
    \textbf{\textit{Technologies:}} ReactJS, NodeJS, Angular, MySQL, MongoDB, Docker, Git, Jenkins, Cloud Services.\\


    \hspace{2cm}\textbf{\textbullet{} FPT Software HCM } {– Full-stack Developer intership} \hfill \textit{Dec 2020 - Aug 2021} \\
    \textbf{\textit{Description:}} Building a recruitment processing and personnel management system for CKHR Consulting Company, include 3 parts: 
        \begin{itemize}[label={-}, leftmargin=1cm, itemsep=-0.2em]
            \item Company page: basic human resource management functions, recruitment planning, candidate management and interview scheduling, process candidate profile/CV according to Applicant Tracking System (ATS) standard procedures.
            \item Recruitment page: (get ideas similar to topcv.vn), with functions such as viewing job postings, applying for jobs, tracking the application process, receiving interview schedules.
            \item Admin page: for manage the entire application.
        \end{itemize}
        \textbf{\textit{Responsibilities:}}
            \begin{itemize}[label={-}, leftmargin=1cm, itemsep=-0.2em]
                \item Analyze, brainstorm, design interfaces for applications with Figma and Photoshop.
                \item Be responsible for the entire Frontend side of the application (design, implement, testing, deployment).
                \item Lead the technical team (4 members), manage, schedule, and assign work to team members, support team with problem solving (both technical and other issues).
                \item Collaborate in database design and construction, assist in writing performance-optimized queries.
                \item Deploy applications to production environment using cloud services (Microsoft Azure, Digital Ocean, Vercel).
                \item Manage team members, quantify, and allocate tasks follow Agile process and Scrum methodologies, daily reports.
                \item Documented for the application.
            \end{itemize}
        \textbf{\textit{Technologies:}} ReactJS, NodeJS, MySQL, MongoDB, Webpack, Redux Toolkit, React-Query, SCSS, Tailwind CSS, Material UI, Google map API, Firebase services (storage, notification, schedule), Docker.


\end{document}
